Characterizing Signal Loss, Error, and Bias in the 21cm Reionization \\Power Spectrum: A Revised Study of PAPER-64

### 2018-01-22 PAPER.tex
covariance language edits in 3.1

To conclude this method, we also show power spectrum results for fringe-rate filtered PAPER-64 data before and after signal 
loss estimation in Figure \ref{fig:ps2_data}, using empirically estimated inverse covariance weighting. The blue dashed line represents the unweighted 
power spectrum $2\sigma$ upper limit, which is identical in both panels (an important check, as we expect no signal loss for this case). The black and 
gray points are positive and negative power spectrum values plotted with $2\sigma$ error bars. Prior to signal loss estimation, it 
is clear that the power spectrum is unfeasible because it is well below the theoretical noise level prediction (solid green curve). 
Post-estimation, the power spectrum errors are higher than both the theory and unweighted power spectrum, a consequence of not being able to characterize covariances well using the time-averaged fringe-rate filtered data (there is less independent information to use). We elaborate on this point in the next section, as well as investigate alternate 
weighting schemes to inverse covariance weighting, with the goal of finding one that balances the aggressiveness of down-weighting contaminants with minimizing the loss of EoR signal.

@@

We saw in Section \ref{sec:otherweight} how limiting the number of down-weighted eigenmodes (i.e. flattening out part of the 
eigenspectrum) can help minimize signal loss. We experiment with this idea on PAPER-64 data, dialing the number of modes 
that are down-weighted from zero (which is equivalent to identity-weighting, or the unweighted case) to $21$ (which is full inverse 
covariance weighting of our $21$ channels). The power spectrum results for one $k$ value, both before and after signal loss 
estimation, are shown in the top panel in Figure \ref{fig:sigloss_modeloop}. We see that the amount of signal loss increases as weighting 
becomes more aggressive (gray curve). In other words, more `weak' (EoR-dominated) fluctuations are being overfit and 
subtracted as more modes are down-weighted. We also find that the power spectrum upper limit, post signal loss estimation, 
increases with the number of down-weighted modes (black curve). Because our data is fringe-rate filtered, we have less information to characterize the covariance matrix and therefore do a worse job estimating it. Hence, the more modes we use in down-weighting, the greater the error we have in estimating the power spectrum.

>>>>

To conclude this method, we also show power spectrum results for fringe-rate filtered PAPER-64 data before and after signal 
loss estimation in Figure \ref{fig:ps2_data}, using empirically estimated inverse covariance weighting. The blue dashed line represents the unweighted 
power spectrum $2\sigma$ upper limit, which is identical in both panels (an important check, as we expect no signal loss for this case). The black and 
gray points are positive and negative power spectrum values plotted with $2\sigma$ error bars. Prior to signal loss estimation, it 
is clear that the power spectrum is unfeasible because it is well below the theoretical noise level prediction (solid green curve). 
Post-estimation, the power spectrum errors are higher than both the theory and unweighted power spectrum, a consequence of weighting with a steep eigenspectrum where the `weak' modes are strongly coupled to the time-averaged fringe-rate filtered data. We elaborate on this point in the next section, as well as investigate alternate 
weighting schemes to inverse covariance weighting, with the goal of finding one that balances the aggressiveness of down-weighting contaminants with minimizing the loss of EoR signal.

@@

We saw in Section \ref{sec:otherweight} how limiting the number of down-weighted eigenmodes (i.e. flattening out part of the 
eigenspectrum and effectively de-coupling the `weak' eigenmodes from the data) can help minimize signal loss. We experiment with this idea on PAPER-64 data, dialing the number of modes 
that are down-weighted from zero (which is equivalent to identity-weighting, or the unweighted case) to $21$ (which is full inverse 
covariance weighting of our $21$ channels). The power spectrum results for one $k$ value, both before and after signal loss 
estimation, are shown in the top panel in Figure \ref{fig:sigloss_modeloop}. We see that the amount of signal loss increases as weighting 
becomes more aggressive (gray curve). In other words, more `weak' (EoR-dominated) fluctuations are being overfit and 
subtracted as more modes are down-weighted. We also find that the power spectrum upper limit, post signal loss estimation, 
increases with the number of down-weighted modes (black curve). The more modes we use in down-weighting, the stronger the coupling between the weighting and the data, and the greater the error we have in estimating the power spectrum.
